%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[letter,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%font and icon packages
\usepackage{wasysym}


%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Mojtaba Alehosseini} \\[7.5pt]
\href{mailto:alehoseini.mojtaba@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ \color{black}Alehoseini.Mojtaba@gmail.com} \ $|$ \ 
\href{https://github.com/Mojtaba-Alehosseini}{\raisebox{-0.05\height}\faGithub\ \color{black} Mojtaba-Alehosseini}  \ $|$ \ 
\href{https://Mojtaba-Alehosseini.github.io}{\faGithubSquare \ \color{black} GitHub.io} \ $|$ \ 
\href{https://linkedin.com/in/Mojtaba-Alehosseini}{\raisebox{-0.05\height}\faLinkedin\ \color{black}Mojtaba-Alehosseini}
%\href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
%\href{tel:+000000000000}{\raisebox{-0.05\height}\faMobile \ +00.00.000.000} \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
%2022 - present & MSc Computer Science (Data Mining) at \textbf{Shaid Beheshti University/Iran} \\

% \faGraduationCap
2017 - 2022 \normalsize \hspace{1cm}  B.Sc. Computer Science at \emph{Yazd University/Iran} \\

Selected Courses:   \hfill (GPA: 17/20) \\ 
\scriptsize \hspace{3cm} Advanced Programming (Grade: 19), Theory of Computation (Grade: 18.25), Operating Systems (Grade: 18.5),\\
\scriptsize \hspace{3cm} Artificial intelligence (Grade: 17), Computer Networks (Grade: 18.1), Computer Simulation (Grade: 17.75),\\
\scriptsize \hspace{3cm} General Mathematics III (Grade: 19), Linear Optimization (Grade: 17.5), Linear Algebra (Grade: 14.25),\\
\scriptsize \hspace{3cm} Data Mining (Grade: 15.75), Databases (Grade: 16.25), Algorithms (Grade: 14.5), Data Structures (Grade: 15),\\
\scriptsize \hspace{3cm} Complex Analysis (Grade: 16), Differential Equations (Grade: 16), General Physics I (Grade: 19.25)\\

\end{tabularx}



%----------------------------------------------------------------------------------------
% Interest
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Interests}
Machine learning, Deep learning, Big data, Data Analysis, Blockchain, Web3, and Distributed Systems.\\

%\setlength{\tabcolsep}{1pt}
\vspace{-0.5cm}


%Projects
\section{Selected Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }


Identification of pneumonia based on a deep learning approach.  \href{https://github.com/mojtaba96/Pneumonia_X_ray_transfer_learning}{\faGithub} \\
\footnotesize \hspace{1cm} Implemented convolutional neural network, using different architectures like VGG, ResNet, NASnet.\\[3.75pt]


Implementing and investigating the performance of classification algorithms such as decision tree,\\
K-nearest neighbor, logistic regression and random forest to:\\
\hspace{1cm}Predict whether a person requires Covid test using these symptoms.\href{https://github.com/mojtaba96/Covid-19}{\faGithub}\\
\hspace{1cm}Classifying patients with liver problems in a clinical data set.   \href{https://github.com/mojtaba96/ILPD-Data-Mining}{\faGithub}\\
\hspace{2cm}\footnotesize  Experimenting and identified best features for different algorithms.\\
\hspace{2cm}\footnotesize  Performing data normalization using different methods (Min-Max, z-score).\\
\hspace{2cm}\footnotesize  Performing N-fold cross-validation on the data set.\\
\hspace{2cm}\footnotesize  Comparing precision, recall and F-score of the algorithms.\\[3.75pt]


Developing a System Modeling and Simulation for:\\
\hspace{2cm}Newspaper Seller's Problem \footnotesize using VBA in Office Excel. 
\href{https://github.com/mojtaba96/Newspaper-Seller-s-Problem}{\normalsize \faGithub} \\
\hspace{2cm}Replacing Bearings in a Milling Machine \footnotesize using Python in Jupyter notebook. 
\href{https://github.com/mojtaba96/Replacing-Bearings-in-a-Milling-Machine}{\normalsize \faGithub} \\
\hspace{2cm}The Dump Truck Problem \footnotesize using VBA in Office Excel.  \href{https://github.com/mojtaba96/The-Dump-Truck-Problem}{\normalsize \faGithub}
\\[3.75pt]


Implementing the Genetic Algorithm and particle swarm optimization \href{https://github.com/mojtaba96/Genetic-Algorithm}{\faGithub}\\
\hspace{1cm}\footnotesize in Matlab and Python with the aim of applying them to the search of the optimum solution of multiple complex functions. \\[3.75pt]

Advanced implementation of regression modelling techniques  like lasso regression in Python.   \href{https://github.com/mojtaba96/Multiple_Regression_Lasso_Regression}{\faGithub} \\[3.75pt]

Implementing the Topic analysis technique in natural language processing.   \href{https://github.com/mojtaba96/NLP}{\faGithub} \\[3.75pt]

Implementation of CNN using Keras for classification of MNIST dataset.   \href{https://github.com/mojtaba96/mnist}{\faGithub} \\[3.75pt]

Implementation of rgb2gray to convert RGB image to grayscale without using OpenCV.  \href{https://github.com/mojtaba96/rgb2gray}{\faGithub} \\[3.75pt]

Implementation of a smart contract on the Goerli Testnet Network with Solidity.  \href{https://github.com/Mojtaba-Alehosseini/Smart-Contract}{\faGithub}\\[3.75pt]

Using a Cryptography library to \footnotesize generate private and public keys, sign and validate the signature, and mine a block.  \href{https://github.com/Mojtaba-Alehosseini/Cryptography}{\normalsize \faGithub} \\[3.75pt]

%Translation of motion into object (motion of a mouse depicting a number) using Python. \\[3.75pt]

%Implementing a chat box interface to the networking connection of two computers. \href{https://github.com/mojtaba96/computer-network}{\faGithub}\\[3.75pt]


Strassen's Matrix Multiplication Algorithm with C++.  \href{https://github.com/mojtaba96/simple-Strassen-Matrix-Multiplication}{\faGithub} \\[3.75pt]

Deriving data structure to eliminate vertices in a tree structure. \href{https://github.com/mojtaba96/Transaction-Optimization}{\faGithub} \\[3.75pt]

%Optimally threaded execution of an OS-like program. \\[3.75pt]

%Developing a probability calculator function for a coin tossing game.   \href{https://github.com/mojtaba96/Coin-Tossing-Game}{\faGithub} \\[3.75pt]

Deriving and implementing a gym registration software \footnotesize using SQL as the database and C\# in Visual Studio. \\[3.75pt]

Developing a restaurant software with C++  \footnotesize to scan and analyze daily transaction data files.
\href{https://github.com/mojtaba96/Restaurant-Management}{\normalsize \faGithub} \\[3.75pt]

%\textbf{Developed a phonebook software with C++.}   \href{https://github.com/mojtaba96/Phonebook}{\faGithub} \\[3.75pt]


\end{tabularx}


%Language scores
\section{Language Scores}
\textbf{TOEFL IBT: 99 out of 120} (Reading: 28, Listening: 26, Speaking: 20, Writing: 25)\\

%\setlength{\tabcolsep}{1pt}
\vspace{-0.5cm}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Industry Knowledge} &  \normalsize{Machine Learning, Operating Systems, Computer hardware expertise}\\
\textbf{Programming Languages}  &  \normalsize{C++, C, Python, MATLAB }\\ 
\textbf{General} &  \normalsize{\LaTeX  ,Microsoft Excel, Microsoft office}\\ 
\textbf{Soft Skills} &  \normalsize{Teamworking, Teaching, Self-Learning, Problem-Solving, Deep work.}\\ 
\end{tabularx}



%Experience
\section{Work Experiences}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{System Administrator, Setare Talaee Co., Delijan, Iran} & \hfill 2021 - 2022 \\[1pt]
\multicolumn{2}{@{}X@{}}{As an IT member of Setare Talaee Co. I was responsible for supporting, troubleshooting, and maintaining computer servers and networks.} \\
\end{tabularx}
\vspace{-0.1cm}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{I was the co-founder of Pinfopedia,} which is a startup company in the field of IT and commercial \\
data sorting and holograming. \\
\end{tabularx}
\vspace{-0.3cm}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Network administrator assistant at Yazd University, Yazd, Iran} & \hfill 2018 - 2019 \\
\end{tabularx}

%\vspace{-0.1cm}

%\begin{tabularx}{\linewidth}{ @{}l r@{} }
%\textbf{Riggosaurus mining}  (a mining project which used graphical data processing in sequences with the \\
%aim of selecting the optimal cryptocurrency to mine at a given time interval).\\
%\end{tabularx}

\vspace{-0.2cm}
%----------
%Teaching Assistant Experience
%----------

%TA
\section{Teaching Assistant Experiences}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
Advanced Programming & \hfill Yazd University, Fall 2020 \\[0pt]
\end{tabularx}
\vspace{-0.7cm}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
Introduction to Programming & \hfill Yazd University, Fall 2019 \\
\end{tabularx}
\vspace{-0.5cm}



%----------
%Other activities 
%----------

%Other activities
\section{Other activities}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Secretary of Scientific Computer Science Association of Yazd University for 2 years.}\\
\footnotesize Our association was named the 2nd best scientific association in Yazd University. I held and managed lots of contests.\\


\end{tabularx}
%\vspace{-0.7cm}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{The scientific editor of DigiaTech} \footnotesize (which was a journal published by the scientific association of computer\\
\footnotesize sciences of Yazd University). I published a review article on machine learning methods and another one on data mining.\\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{The Translator of SimPy library manual (from English to Persian).}  \href{https://github.com/mojtaba96/Persian-Translation-of-Simpy}{\faGithub} \\
\end{tabularx}

%\vspace{-0.2cm}

%----------
%Honors & Awards
%----------

%Awards
\section{Honors and Awards}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Ranked in the top 2\%} of nearly 500,000 participants in the nationwide university entrance exam, 2017.\\
\end{tabularx}

\vspace{-0.2cm}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Ranked the 3rd} highest scoring student of computer sciences of Yazd University, 2021 \\
\end{tabularx}

%\vspace{-0.3cm}

%----------
%References
%----------

%Awards
\section{References}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Dr. Jamal Zarepour} \href{https://pws.yazd.ac.ir/jzarepour/}{\faIcon{external-link-alt}}
\href{https://scholar.google.com/citations?user=7P3JZ8IAAAAJ}{\faIcon{graduation-cap}}\\
\hspace{0.9cm}Assistant Professor, Head of Yazd University Computer Science Department, Yazd, Iran \\
\hspace{0.9cm}Email Address: \href{mailto:zarepourjamal@yazd.ac.ir}{zarepourjamal@yazd.ac.ir} \\
\end{tabularx}

\vspace{-0.1cm}

\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Dr. Saeid Alikhani} \href{https://pws.yazd.ac.ir/alikhani/}{\faIcon{external-link-alt}}
\href{https://scholar.google.com/citations?user=Eo9TBCgAAAAJ}{\faIcon{graduation-cap}}\\
\hspace{0.9cm}Professor of Mathematics, Chair of School of Mathematical Sciences, Yazd University, Yazd, Iran \\
\hspace{0.9cm}Email Address: \href{mailto:alikhani@yazd.ac.ir}{alikhani@yazd.ac.ir} \\
\end{tabularx}


%\vspace{-0.1cm}
%\begin{tabularx}{\linewidth}{ @{}l X@{} }
%\href{https://yazd.ac.ir/people/e.abbasi/}{\textbf{\color{black}Dr. Elham Abbasi}}\\
%\hspace{0.9cm}Assistant Professor of Computer Science Department, Yazd University, Yazd, Iran \\
%\hspace{0.9cm}Email Address: \href{mailto:e.abbasi@yazd.ac.ir}{e.abbasi@yazd.ac.ir} \\
%\end{tabularx}

%\vspace{-0.1cm}
%\begin{tabularx}{\linewidth}{ @{}l X@{} }
%\textbf{Dr. Sepehr Ebrahimi Mood} \href{https://yazd.ac.ir/en/people/s.ebrahimi}{\faIcon{external-link-alt}}
%\href{https://scholar.google.com/citations?user=NxO3-dMAAAAJ}{\faIcon{graduation-cap}}\\
%\hspace{0.9cm}Assistant Professor, Mathematical Sciences Department - Computer Sciences, Yazd University, Yazd, Iran \\
%\hspace{0.9cm}Email Address: \href{mailto:s.ebrahimi@yazd.ac.ir}{s.ebrahimi@yazd.ac.ir} \\
%\end{tabularx}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
%\section{Publications}
%\begin{refsection}[citations.bib]
%\nocite{*}
%\printbibliography[heading=none]
%\end{refsection}


%\vfill
%\center{\footnotesize Last updated: \today}

\end{document}
